---
title: "Library Partnership - IDW"
author: "Corey DeGroot"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---

Methodology
==================================


Library Size Estimate

- Collection Space = $13*(N_b+N_v+N_a)+(45*N_i)$
    - $N_b =$ Number of books
    - $N_v =$ Number of serial volumes
    - $N_a =$ Number of audio visual materials
    - $N_i =$ Number of internet terminals
    
- Work Space = $150*N_w+30*N_s/1000$
    - $N_w =$ Number of workstations
    - $N_s =$ Number of seats

- Lbrary Size = Collection Space + Work Space


Analysis

- Inverse-Distance-Weighted (IDW) Average
    - Tobler’s First Law: “All things are related, but nearby things are more related than distant things”
    - Uses known values to estimate value at nearby points
    - Library index estimates the value of the libraries surrounding the installation
    
- $z(x) = \frac{\sum_{i=1}^{n}W_i * Z_i}{\sum_{i=1}^{n}W_i}$

    - $W_i = 1/d_i^2$

    - $Z_i =$ Size of the library 
    


```{r eval=TRUE}
absolutePanel(tags$img(src = "IDW.png", height = "600px"),
              top = "200px",
              left = "1000px"
)

```


Analysis
======================================


```{r global, include=FALSE}
library(flexdashboard)
library(data.table)
library(leaflet)
library(DT)

IDW_straight <- read.table("C:/Files/Documents/R/publicLibs/inst/extdata4/IDW/Straight.txt", header = TRUE, stringsAsFactors = F)
IDW_drive <- read.table("C:/Files/Documents/R/publicLibs/inst/extdata4/IDW/Drive.txt", header = TRUE, stringsAsFactors = F)

IDW_straight <- IDW_straight[-c(2, 19, 21, 28),]
colnames(IDW_straight) <- c("Base Name", "Short Name", "Abbr", "Long", "Lat", "5 Miles", "10 Miles", "15 Miles", "20 Miles",
                               "25 Miles", "30 Miles", "35 Miles", "40 Miles", "45 Miles", "50 Miles", "55 Miles", "60 Miles",
                               "65 Miles", "70 Miles", "75 Miles", "80 Miles", "85 Miles", "90 Miles", "95 Miles", "100 Miles")

IDW_drive <- IDW_drive[-c(2, 19, 21, 28),]
colnames(IDW_drive) <- c("Base Name", "Short Name", "Abbr", "Long", "Lat", "5 Miles", "10 Miles", "15 Miles", "20 Miles",
                               "25 Miles", "30 Miles", "35 Miles", "40 Miles", "45 Miles", "50 Miles", "55 Miles", "60 Miles",
                               "65 Miles", "70 Miles", "75 Miles", "80 Miles", "85 Miles", "90 Miles", "95 Miles", "100 Miles")

Base_Locs <- read.table("C:/Files/Documents/R/publicLibs/inst/extdata/Base_Locations.txt", header = TRUE, stringsAsFactors = F)
Base_Locs <- Base_Locs[-c(2, 19, 21, 28),]



```


Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
  sliderInput(inputId = "rad", label = "Radius Around the Base:",
              min = 5, max = 100, value = 50,
              step = 5)
  
  selectInput(inputId = "base", label = "Installation:",
              choices = Base_Locs[,1], selected = NULL)
  
  selectInput(inputId = "mode", label = "Distance Mode:",
              choices = c("Straight Line Distance", "Driving Distance"),
              selected = NULL)
```

Insert text about the app...
  
Row {data-height=550}
-----------------------------------------------------------------------

### Map

```{r}


  
output$basemap <- renderLeaflet({
  
  base.loc <- Base_Locs[which(Base_Locs[,1]%in%input$base),]
  file.location <- "C:/Files/Documents/R/publicLibs/inst/extdata4/App Data/Base Libs/"
  inst <- as.character(input$base)
  base_lib <- read.table(paste(c(file.location, IDW_straight[which(IDW_straight[, 1] == inst), 3], "_Libs.txt"), collapse = ""), 
                         header = TRUE, stringsAsFactors = FALSE)
  colnames(base_lib) <- c("Library Name", "Service Area Population", "Address", "Latitude", "Longitude", "Central Libraries",
                          "Branch Libraries", "Total Staff", "Print Materials", "Audio Materials", "Video Materials", "Print Serials",
                          "Computers", "Collection Space", "Seats Per", "Work Space", "Size", "Distance", "Weight", "SizeWeight",
                          "Drive Distance", "Drive Weight", "Drive SizeWeight")
  base_lib <- subset(base_lib, base_lib[, "Distance"] <= input$rad)
  
  # redStar <- makeIcon(
  #   iconUrl <- "C:/Files/Documents/R/publicLibs/inst/extdata4/App Data/red_star.png",
  #   iconWidth <- 10, iconHeight <- 40,
  #   iconAnchorX <- 22, iconAnchorY <- 94,
  # )
  
  leaflet() %>%
    addTiles() %>%
    addCircleMarkers(base_lib$Longitude,
                     base_lib$Latitude,
                     color = "blue",
                     radius = 6,
                     fill = T,
                     fillOpacity = 1,
                     opacity = 1,
                     popup = paste(base_lib$`Library Name`, "<br>",
                                   base_lib$Address)) %>%

    addCircleMarkers(base.loc$Longitude,
                     base.loc$Latitude,
                     color = "red",
                     radius = 6,
                     fill = T,
                     fillOpacity = 1,
                     opacity = 1,
                     popup = base.loc$Base..Long.Name.) %>%
  
    # addMarkers(base_lib$Longitude,
    #            base_lib$Latitude,
    #            popup = base_lib$Address) %>%

    # addMarkers(base.loc$Longitude,
    #            base.loc$Latitude,
    #            popup = base.loc$Base..Abbreviation.,
    #            icon = redStar) %>%
    
    addLegend("bottomleft",
              title = "Legend",
              colors = c("Red", "Blue"),
              labels = c("Air Force Base", "Library"),
              opacity = 1)
})


leafletOutput("basemap", width = "100%", height = "100%")

# fitBounds(-127.44,24.05,-65.30,50.35) %>% 

```

### IDW Measure

```{r}
  
IDWData <- reactive({
  
  if(input$mode == "Straight Line Distance" ) {
    CONUS_Locations <- IDW_straight
  }
    else {
      CONUS_Locations <- IDW_drive
    }
  
  IDW <- as.data.table(CONUS_Locations)
  var <- paste(input$rad, "Miles")
  IDW <- IDW[order(-IDW[[var]])][,"Overall Rank" := 1:.N]
  IDW <- as.data.frame(IDW)
  IDW <- IDW[, c("Base Name", paste(as.character(input$rad), "Miles"), "Overall Rank")]
  
  
})

  renderTable(IDWData(), digits = 3)

```

Row {data-height=450}
-----------------------------------------------------------------------

### Library List

```{r}

  file.location <- "C:/Files/Documents/R/publicLibs/inst/extdata4/App Data/Base Libs/"

  selectedData <- reactive({
    
    
    
    inst <- as.character(input$base)
    base_lib <- read.table(paste(c(file.location, IDW_straight[which(IDW_straight[, 1] == inst), 3], "_Libs.txt"), collapse = ""),
                           header = TRUE, stringsAsFactors = FALSE)
    colnames(base_lib) <- c("Library Name", "Service Area Population", "Address", "Latitude", "Longitude",
                            "Central Libraries", "Branch Libraries", "Total Staff", "Print Materials",
                            "Audio Materials", "Video Materials", "Print Serials", "Computers", "Collection Space",
                            "Seats Per", "Work Space", "Size", "Distance", "Weight", "SizeWeight", "Drive Distance",
                            "Drive Weight", "Drive SizeWeight")
    
    if(input$mode == "Straight Line Distance" ) {
      
      col <- c("Library Name", "Service Area Population", "Central Libraries", "Branch Libraries",
               "Total Staff", "Print Materials", "Audio Materials", "Video Materials", "Print Serials",
               "Computers", "Collection Space", "Seats Per", "Work Space", "Size", "Distance", "Weight", "SizeWeight")
      libs_straight <- base_lib[, paste(col)]
      base_lib.sub <- subset(libs_straight, libs_straight[, "Distance"] <= input$rad)
      base_lib.sub <- as.data.table(base_lib.sub)
      base_lib.sub <- base_lib.sub[order(base_lib.sub$Distance)]
      base_lib.sub <- as.data.frame(base_lib.sub)
      
  #     var <- paste(input$rad, "Miles")
  # IDW <- IDW[order(-IDW[[var]])]
    }
    else {
      col <- c("Library Name", "Service Area Population", "Central Libraries", "Branch Libraries",
               "Total Staff", "Print Materials", "Audio Materials", "Video Materials", "Print Serials",
               "Computers", "Collection Space", "Seats Per", "Work Space", "Size", "Distance", "Drive Distance", 
               "Drive Weight", "Drive SizeWeight")
      libs_drive <- base_lib[, paste(col)]
      base_lib.sub <- subset(libs_drive, libs_drive[, "Distance"] <= input$rad)
      base_lib.sub <- as.data.table(base_lib.sub)
      base_lib.sub <- base_lib.sub[order(base_lib.sub$'Drive Distance')]
      base_lib.sub <- as.data.frame(base_lib.sub)
      
    }
    
    
    
    # datatable(base_lib.sub, rownames = FALSE, extensions = 'Scroller',
    #       options = list(scrollY = 200, scroller = TRUE, columnDefs = list(list(className = 'dt-left', targets = 0:3))))
  })


  renderTable(selectedData(), digits = 2)
  
  
  
  

## options=list(scrollX=TRUE, scrolly = TRUE)
 

```


